Learning constraints in tabular data

### 2016-05-19 Paper/ECAI/tabular.tex
update steps based on feedback from Luc

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into type-consistent contiguous \textit{superblocks}
\item Generate for each constraint all valid argument assignments:
\begin{enumerate}
\item For each constraint, generate all candidate \textit{super-assignments} by selecting compatible superblocks for each argument
\item For each candidate super-assignment, generate all valid argument assignments from the superblocks.
\end{enumerate}
\end{enumerate}

>>>>

Our proposed methodology contains the following steps:
\begin{enumerate}
\item Extract headerless tables from tabular data
\item Partition the tables into maximally contiguous, type-consistent \textit{superblocks}
\item Generate for each constraint all valid argument assignments:
\begin{enumerate}
\item For each constraint $c$, generate all atoms $c(B_1, \ldots ,B_n)$ where each $B_i$ is a maximal \textit{superblock} and the $B_i$ are compatible with the signature.
\item For each generated atom $c(B_1, \ldots ,B_n)$, find all valid $c(B'_1, \ldots, B'_n)$ such that $\forall i, B'_i \sqsubseteq B_i$ and the signature and definition of $c(B'_1, \ldots, B'_n)$ is satisfied.
\end{enumerate}
\end{enumerate}
